%% FIELD WORK %%
\section{Field Experience}

% todo this needs to be updated once completed
% \field[
%     layout=3,
%     activity=Seismic Node \& Infrasound Recoveries,
%     who={University of Oregon \& USGS Cascades Volcano Observatory},
%     location={Mt. St. Helens, WA},
%     date=Oct. 2025,
%     length={TBD},
% ]{
%     \begin{cvitemize}
%         \item Will assist in the recovery of infrasound, field cameras, \& seismic nodes in a helicopter-enabled mission on Mt. St. Helens.
%         % \item Joint effort organized by the University of Oregon, \& Cascades Volcano Observatory.
%         % \item Hiked \& bushwhacked 3 mi day 1, 11 mi day 2
%     \end{cvitemize}
% }

\field[
    layout=3,
    activity=Seismic Node Recovery/Redeploy,
    who={University of Oregon \& USGS Cascades Volcano Observatory},
    location={Mt. Rainier \& Mt. St. Helens, WA},
    date=Sep 2025,
    length={3 days},
]{
    \begin{cvitemize}
        \item Assisted in the recovery of seismic nodes deployed in Aug 2025 along the Tahoma Creek drainage on Mt. Rainier.
        \item Assisted in the deployment of infrasound, field cameras, \& 87 seismic nodes in a helicopter-enabled mission on Mt. St. Helens.
        % \item Joint effort organized by the University of Oregon, \& Cascades Volcano Observatory.
        % \item Hiked \& bushwhacked 3 mi day 1, 11 mi day 2
    \end{cvitemize}
}

\field[
    layout=3,
    activity=PACSAFE 2025 \& EXTEND 2025,
    who={NRCAN, University of British Columbia, University of Victoria, NFSI},
    location={Offshore, BC},
    date=Aug 2025, % 6--25
    length={20 days},
]{
    \begin{cvitemize}
        \item Partcipated as an Apply-to-Sail student aboard the CCGS John P. Tully to recover \& deploy ocean bottom seismometers (OBS) along the Explorer microplate off of Haida Gwaii and at the Endeavour ridge. % for the 2025 legs of both the PACSAFE \& EXTEND projects.
        % \item PACSAFE OBS were recovered along the Explorer microplate off of Haida Gwaii \& redeployed to the south of the 2024 field.
        % \item EXTEND OBS were deployed along at Endeavour to complement existing cabled arrays.
    \end{cvitemize}
}

\field[
    layout=3,
    activity=Temporary Seismic Array Deployment,
    who={University of Oregon \& USGS Cascades Volcano Observatory},
    location={Mt. Rainier National Park, WA},
    date=Jul 2025, % 28 & 29
    length={2 days},
]{
    \begin{cvitemize}
        \item Assisted a deployment of 53 seismic nodes in temporary arrays along the Tahoma Creek drainage to support studies of debris flows.
        % \item Joint effort organized by UC Davis, the University of Oregon, \& Cascades Volcano Observatory.
        % \item Hiked \& bushwhacked 3 mi day 1, 11 mi day 2
    \end{cvitemize}
}


\field[
    layout=3,
    activity=Field Assistant,
    who=UC Davis,
    location={Jot Dean Cave \& Pluto Cave, CA},
    date=May 2025,
    length={1 day},
]{
    \begin{cvitemize}
        \item Assisted in the collection of biofilm samples from lava tubes.
    \end{cvitemize}
}

\field[
    layout=3,
    activity=Graduate Volcanology Seminar,
    who=McGill University,
    location={Long Valley Caldera, CA},
    date=Oct 2022,
    length={7 days},
    % link=https://www.eps.mcgill.ca/~stix/lvc/story.pdf,
]{
    \begin{cvitemize}
        \item Participated in a field seminar to study the volcanological features \& geologic history of the caldera \& associated features.
    \end{cvitemize}
}

\field[
    layout=3,
    activity=Field School I,
    who=McGill University,
    location={Death Valley, CA},
    date=May 2021, %\daterange{2021/05/01}{2021/05/17},
    length={16 days},
]{
    \begin{cvitemize}
        \item Produced maps of geologic units \& structures in both Rainbow Basin \& Dublin Gulch, CA.
        % \item Mapped soil carbon in the High Sierra Nevada Mountains.
        \item Gained experience in structural field mapping, using a Brunton compass, \& navigating with topographic maps.
    \end{cvitemize}
}